Exploring the Design Space of Differentially Private Bayesian Inference under Hellinger Distance

### 2019-01-23 ICML2019/main.tex
tweak

\appendix

\noindent \textbf{Theorem \ref{thm_gamma_smooth}.}
\emph{
Given data set $\dataobs$, the $\gamma -$smooth sensitivity of Bayesian inference process w.r.t. the Hellinger distance $S(\dataobs)$ satisfying:%\\
whenever $\adj{\dataobs}{\dataobs'}$, 
%\begin{equation}
%\label{eq_gamma_smooth}
$\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma$.
}

\begin{proof}
of Theorem. \ref{thm_gamma_smooth}.\\
For $\adj{\dataobs}{\dataobs'}$ and arbitrary $\dataobs'' \in \{0,1\}^{n}$:\\
From Equation (\ref{eq_smooth}), we can get:
\[
\frac{1}{S(\dataobs)} 
 = \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{ \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'') \bigg \}\\
\]

Since $d(\dataobs,\dataobs'') \leq d(\dataobs,\dataobs') + d(\dataobs',\dataobs'') \leq 1 + d(\dataobs',\dataobs'')$:

\begin{equation*}
\begin{split}
& \leq \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{  \frac{1}{LS(\dataobs'')} +\gamma \cdot (1 + d(\dataobs',\dataobs'')) \bigg \}\\
& = \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{
\gamma + \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs',\dataobs'')\bigg 
\}\\
& = \gamma + \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{
\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs',\dataobs'')\bigg
\}\\
& = \gamma + \frac{1}{S(\dataobs')}
\end{split}
\end{equation*}
Then we can get:
$\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma.$
\end{proof}

\noindent \textbf{Lemma \ref{lem_loc_opt}.}
\emph{
\[
LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer{\dataobs}, \bysinfer(\dataobs')).
\]
}

\begin{proof} of Lemma \ref{lem_loc_opt}.\\
For any $r \in \mathcal{R}$ and $\dataobs' \in \datauni^n$ with $\adj{\dataobs}{\dataobs'}$, we have
\begin{align*}
&\lvert \hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer(\dataobs'), r)\rvert\\
& = 
\begin{cases}
\hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer(\dataobs'),r) & \text{positive case}\\
\hellinger(\bysinfer(\dataobs'),r) - \hellinger(\bysinfer{\dataobs}, r) & \text{negative case}
\end{cases}\\
& \leq 
\begin{cases}
\hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})+
\hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'),r) & \\
\hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})+
\hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer{\dataobs}, r)&
\end{cases}\\
&= \hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})
\end{align*}
The equality holds if $r = \bysinfer{\dataobs}$ or $r = \bysinfer(\dataobs')$.
Hence, we conclude the statement of this lemma.
\end{proof}

\noindent \textbf{ Lemma \ref{lem_hexpmech_privacy}. } 
\emph{
$\hexpmech$ is $\epsilon$-differential privacy by setting $\gamma = 1.0$.
}

\begin{proof} of Lemma \ref{lem_hexpmech_privacy}.\\
  By Definition \ref{def_epsilon_dp}, to proof Lemma \ref{lem_hexpmech_privacy}, we need to prove:\\
  For any $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$ and any beta distribution $r$:
  \begin{equation*}
  \hexpmechPr{\dataobs}{z = r} \leq e^{\epsilon} \hexpmechPr{\dataobs'}{z = r}. 
  \end{equation*}
  By definition \ref{def_smoo_2}:
  \begin{equation*}
  \begin{split}
  \hexpmechPr{\dataobs}{z = r} 
  & = \frac {\exp\big(\frac{-\epsilon\cdot\ux{r}}{4\cdot S(\dataobs)}\big)}{\unomalizer{\dataobs}} \\
  & = \frac {\exp\big(
  \frac{-\epsilon\cdot(\ux{r} + \uxadj{r} - \uxadj{r})}{4\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}} \\
  & = \frac {\exp\big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}}
  \\
  & \cdot \exp\big( \frac{\epsilon\cdot(\uxadj{r} - \ux{r})}{4\cdot S(\dataobs)} \big)\\
  \end{split}
  \end{equation*}
  Because $S(\dataobs) \geq LS(\dataobs) \geq (\uxadj{r} - \ux{r})$:
  \begin{equation*}
  \begin{split}
  & \leq \frac {\exp\big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}}
  \cdot \exp\big( \frac{\epsilon}{4} \big) \\
  & = \exp\big( \frac{\epsilon}{4} \big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
  \big)
  } 
  {\unomalizer{\dataobs}}\\
  & \cdot \exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)\\
  & = \exp\big( \frac{\epsilon}{4} \big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}\\
  & \cdot \exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r})}{4}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
  \big)\\
  \end{split}
  \end{equation*}

  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$:
  \begin{equation*}
  \begin{split}
  & \leq \exp\big( \frac{\epsilon}{4} \big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}\\
  & \cdot \exp
  \big(
  \frac{\epsilon}{4}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
  \big)\\
  \end{split}
  \end{equation*}

  Because the property of $\gamma -$smooth sensitivity: $\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)} \leq \gamma$:  
  \begin{equation*}
  \begin{split}
  & \leq \exp\big( \frac{\epsilon}{4} \big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}
  \exp
  \big(
  \frac{\epsilon}{4} \cdot \gamma
  \big)\\
  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}\\
  \end{split}
  \end{equation*}

  Doing the same transformation in the denominator:
  \begin{equation*}
  \begin{split}
  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\ux{r'} + \uxadj{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)}
  \big)
  }\\
  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \\
  & \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
  \big)
  \exp 
  \big(
  \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)}
  \big)
  }\\
  \end{split}
  \end{equation*}

  Because $S(\dataobs) \geq LS(\dataobs) \geq (\ux{r} - \uxadj{r})$ $\implies$ $ \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)} \geq \frac{-\epsilon}{4}$:
  \begin{equation*}
  \begin{split}
  & \leq \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
  \big)
  \exp 
  \big(
  \frac{-\epsilon}{4}
  \big)
  }\\
  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
  \big)
  }\\
  & \cdot 
  \frac{1}
  {
  \exp 
  \big(
  \frac{-\epsilon}{4}
  \big)
  \exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r'})}{4\cdot S(\dataobs')}
  \big)
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'})}{4\cdot S(\dataobs')}
  \big)
  }\\
  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
  \big)}\\
  & \cdot\frac{1}{
  \exp 
  \big(
  \frac{-\epsilon}{4}
  \big)
  \exp
  \big(
  \frac{- \epsilon\cdot(\ux{r'})}{4}
  (\frac{1}{S(\dataobs)}
-
  \frac{1}{S(\dataobs')})
  \big)
  }
  \end{split}
  \end{equation*}

  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$ $\implies$ $\frac{- \epsilon\cdot(\ux{r'})}{4} \geq  \frac{-\epsilon}{4}$:
  \begin{equation*}
  \begin{split}
  & \leq \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
  \big)}\\
  & \cdot \frac{1}{
  \exp 
  \big(
  \frac{-\epsilon}{4}
  \big)
  \exp
  \big(
  \frac{- \epsilon}{4}
  (\frac{1}{S(\dataobs)}
-
  \frac{1}{S(\dataobs')})
  \big)
  }\\
  \end{split}
  \end{equation*}

  Because the property of $\gamma -$ smooth sensitivity: $\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma$ $\implies$
  $\frac{- \epsilon}{4}
  (\frac{1}{S(\dataobs)}-
  \frac{1}{S(\dataobs')}) \geq \frac{- \epsilon}{4} \cdot \gamma$
  \begin{equation*}
  \begin{split}
  & \leq \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
  \big)
  \exp 
  \big(
  \frac{-\epsilon}{4}
  \big)
  \exp
  \big(
  \frac{- \epsilon}{4} \cdot \gamma
  \big)
  }\\
  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
  \big)
  \exp 
  \big(
  \frac{-\epsilon}{4} +   \frac{- \epsilon}{4} \cdot \gamma
  \big)
  }\\
  & = e^{( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma )} \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \unomalizer{\dataobs'}
  }\\
  & = e^{( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma )} \cdot   \hexpmechPr{\dataobs'}{z = r}
  \end{split}
  \end{equation*}

  Given $\gamma = 1$, $\epsilon - $differential privacy can be achieved by $\hexpmech$.

\end{proof}

\noindent \textbf{ Lemma \ref{lem_acc_lap}.}
\emph{
Given $Y \thicksim \lap{0}{b}$, the accuracy bound developed for $\lapmech$ is:
\begin{align*}
&
\lapmechPr{\dataobs}{
\begin{aligned}
\lefteqn{\hellinger(\bysinfer{\dataobs}, z )}\\ 
&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
\end{aligned}
}
\\
&\qquad = 
\begin{cases}
\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta }} - e^{- \frac{\epsilon (t + 1)}{\Delta }}) &  t \geq 0\\
\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta }} - e^{\frac{\epsilon (t)}{\Delta }}) & t < 0
\end{cases}
\end{align*}
where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer{\dataobs} = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $z = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
}

\begin{proof} of Lemma \ref{lem_acc_lap}.\\
Given $Y \thicksim \lap{0}{b}$, we have\cite{dwork2014algorithmic}:$\Pr[|Y| \geq t \cdot b] = e^{- t}.$\\
Based on this, we get:$\Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{\Delta }}$, where $Y \thicksim \lap{0}{\frac{\Delta }{\epsilon}}$ in our setting.

>>>>

% \appendix

% \noindent \textbf{Theorem \ref{thm_gamma_smooth}.}
% \emph{
% Given data set $\dataobs$, the $\gamma -$smooth sensitivity of Bayesian inference process w.r.t. the Hellinger distance $S(\dataobs)$ satisfying:%\\
% whenever $\adj{\dataobs}{\dataobs'}$, 
% %\begin{equation}
% %\label{eq_gamma_smooth}
% $\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma$.
% }

% \begin{proof}
% of Theorem. \ref{thm_gamma_smooth}.\\
% For $\adj{\dataobs}{\dataobs'}$ and arbitrary $\dataobs'' \in \{0,1\}^{n}$:\\
% From Equation (\ref{eq_smooth}), we can get:
% \[
% \frac{1}{S(\dataobs)} 
%  = \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{ \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'') \bigg \}\\
% \]

% Since $d(\dataobs,\dataobs'') \leq d(\dataobs,\dataobs') + d(\dataobs',\dataobs'') \leq 1 + d(\dataobs',\dataobs'')$:

% \begin{equation*}
% \begin{split}
% & \leq \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{  \frac{1}{LS(\dataobs'')} +\gamma \cdot (1 + d(\dataobs',\dataobs'')) \bigg \}\\
% & = \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{
% \gamma + \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs',\dataobs'')\bigg 
% \}\\
% & = \gamma + \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{
% \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs',\dataobs'')\bigg
% \}\\
% & = \gamma + \frac{1}{S(\dataobs')}
% \end{split}
% \end{equation*}
% Then we can get:
% $\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma.$
% \end{proof}

% \noindent \textbf{Lemma \ref{lem_loc_opt}.}
% \emph{
% \[
% LS(\dataobs) = \max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}} \hellinger(\bysinfer{\dataobs}, \bysinfer(\dataobs')).
% \]
% }

% \begin{proof} of Lemma \ref{lem_loc_opt}.\\
% For any $r \in \mathcal{R}$ and $\dataobs' \in \datauni^n$ with $\adj{\dataobs}{\dataobs'}$, we have
% \begin{align*}
% &\lvert \hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer(\dataobs'), r)\rvert\\
% & = 
% \begin{cases}
% \hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer(\dataobs'),r) & \text{positive case}\\
% \hellinger(\bysinfer(\dataobs'),r) - \hellinger(\bysinfer{\dataobs}, r) & \text{negative case}
% \end{cases}\\
% & \leq 
% \begin{cases}
% \hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})+
% \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'),r) & \\
% \hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})+
% \hellinger(\bysinfer{\dataobs}, r) - \hellinger(\bysinfer{\dataobs}, r)&
% \end{cases}\\
% &= \hellinger(\bysinfer(\dataobs'), \bysinfer{\dataobs})
% \end{align*}
% The equality holds if $r = \bysinfer{\dataobs}$ or $r = \bysinfer(\dataobs')$.
% Hence, we conclude the statement of this lemma.
% \end{proof}

% \noindent \textbf{ Lemma \ref{lem_hexpmech_privacy}. } 
% \emph{
% $\hexpmech$ is $\epsilon$-differential privacy by setting $\gamma = 1.0$.
% }

% \begin{proof} of Lemma \ref{lem_hexpmech_privacy}.\\
%   By Definition \ref{def_epsilon_dp}, to proof Lemma \ref{lem_hexpmech_privacy}, we need to prove:\\
%   For any $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$ and any beta distribution $r$:
%   \begin{equation*}
%   \hexpmechPr{\dataobs}{z = r} \leq e^{\epsilon} \hexpmechPr{\dataobs'}{z = r}. 
%   \end{equation*}
%   By definition \ref{def_smoo_2}:
%   \begin{equation*}
%   \begin{split}
%   \hexpmechPr{\dataobs}{z = r} 
%   & = \frac {\exp\big(\frac{-\epsilon\cdot\ux{r}}{4\cdot S(\dataobs)}\big)}{\unomalizer{\dataobs}} \\
%   & = \frac {\exp\big(
%   \frac{-\epsilon\cdot(\ux{r} + \uxadj{r} - \uxadj{r})}{4\cdot S(\dataobs)}
%   \big)}
%   {\unomalizer{\dataobs}} \\
%   & = \frac {\exp\big(
%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
%   \big)}
%   {\unomalizer{\dataobs}}
%   \\
%   & \cdot \exp\big( \frac{\epsilon\cdot(\uxadj{r} - \ux{r})}{4\cdot S(\dataobs)} \big)\\
%   \end{split}
%   \end{equation*}
%   Because $S(\dataobs) \geq LS(\dataobs) \geq (\uxadj{r} - \ux{r})$:
%   \begin{equation*}
%   \begin{split}
%   & \leq \frac {\exp\big(
%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
%   \big)}
%   {\unomalizer{\dataobs}}
%   \cdot \exp\big( \frac{\epsilon}{4} \big) \\
%   & = \exp\big( \frac{\epsilon}{4} \big) \cdot 
%   \frac {
%   \exp
%   \big(
%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
%   \big)
%   } 
%   {\unomalizer{\dataobs}}\\
%   & \cdot \exp
%   \big(
%   \frac{\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
%   \big)
%   \exp
%   \big(
%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
%   \big)\\
%   & = \exp\big( \frac{\epsilon}{4} \big) \cdot 
%   \frac {
%   \exp
%   \big(
%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
%   \big)
%   } 
%   {\unomalizer{\dataobs}}\\
%   & \cdot \exp
%   \big(
%   \frac{\epsilon\cdot(\uxadj{r})}{4}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
%   \big)\\
%   \end{split}
%   \end{equation*}

%   Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$:
%   \begin{equation*}
%   \begin{split}
%   & \leq \exp\big( \frac{\epsilon}{4} \big) \cdot 
%   \frac {
%   \exp
%   \big(
%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
%   \big)
%   } 
%   {\unomalizer{\dataobs}}\\
%   & \cdot \exp
%   \big(
%   \frac{\epsilon}{4}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
%   \big)\\
%   \end{split}
%   \end{equation*}

%   Because the property of $\gamma -$smooth sensitivity: $\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)} \leq \gamma$:  
%   \begin{equation*}
%   \begin{split}
%   & \leq \exp\big( \frac{\epsilon}{4} \big) \cdot 
%   \frac {
%   \exp
%   \big(
%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
%   \big)
%   } 
%   {\unomalizer{\dataobs}}
%   \exp
%   \big(
%   \frac{\epsilon}{4} \cdot \gamma
%   \big)\\
%   & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
%   \frac {
%   \exp
%   \big(
%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
%   \big)
%   } 
%   {\unomalizer{\dataobs}}\\
%   \end{split}
%   \end{equation*}

%   Doing the same transformation in the denominator:
%   \begin{equation*}
%   \begin{split}
%   & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
%   \frac {
%   \exp
%   \big(
%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
%   \big)
%   } 
%   {
%   \sum_{r'\in \candidateset} 
%   \exp 
%   \big(
%   \frac{-\epsilon\cdot(\ux{r'} + \uxadj{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)}
%   \big)
%   }\\
%   & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \\
%   & \cdot 
%   \frac {
%   \exp
%   \big(
%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
%   \big)
%   } 
%   {
%   \sum_{r'\in \candidateset} 
%   \exp 
%   \big(
%   \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
%   \big)
%   \exp 
%   \big(
%   \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)}
%   \big)
%   }\\
%   \end{split}
%   \end{equation*}

%   Because $S(\dataobs) \geq LS(\dataobs) \geq (\ux{r} - \uxadj{r})$ $\implies$ $ \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)} \geq \frac{-\epsilon}{4}$:
%   \begin{equation*}
%   \begin{split}
%   & \leq \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
%   \frac {
%   \exp
%   \big(
%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
%   \big)
%   } 
%   {
%   \sum_{r'\in \candidateset} 
%   \exp 
%   \big(
%   \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
%   \big)
%   \exp 
%   \big(
%   \frac{-\epsilon}{4}
%   \big)
%   }\\
%   & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
%   \frac {
%   \exp
%   \big(
%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
%   \big)
%   } 
%   {
%   \sum_{r'\in \candidateset} 
%   \exp 
%   \big(
%   \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
%   \big)
%   }\\
%   & \cdot 
%   \frac{1}
%   {
%   \exp 
%   \big(
%   \frac{-\epsilon}{4}
%   \big)
%   \exp
%   \big(
%   \frac{\epsilon\cdot(\uxadj{r'})}{4\cdot S(\dataobs')}
%   \big)
%   \exp
%   \big(
%   \frac{-\epsilon\cdot(\uxadj{r'})}{4\cdot S(\dataobs')}
%   \big)
%   }\\
%   & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
%   \frac {
%   \exp
%   \big(
%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
%   \big)
%   } 
%   {
%   \sum_{r'\in \candidateset} 
%   \exp 
%   \big(
%   \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
%   \big)}\\
%   & \cdot\frac{1}{
%   \exp 
%   \big(
%   \frac{-\epsilon}{4}
%   \big)
%   \exp
%   \big(
%   \frac{- \epsilon\cdot(\ux{r'})}{4}
%   (\frac{1}{S(\dataobs)}
% -
%   \frac{1}{S(\dataobs')})
%   \big)
%   }
%   \end{split}
%   \end{equation*}

%   Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$ $\implies$ $\frac{- \epsilon\cdot(\ux{r'})}{4} \geq  \frac{-\epsilon}{4}$:
%   \begin{equation*}
%   \begin{split}
%   & \leq \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
%   \frac {
%   \exp
%   \big(
%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
%   \big)
%   } 
%   {
%   \sum_{r'\in \candidateset} 
%   \exp 
%   \big(
%   \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
%   \big)}\\
%   & \cdot \frac{1}{
%   \exp 
%   \big(
%   \frac{-\epsilon}{4}
%   \big)
%   \exp
%   \big(
%   \frac{- \epsilon}{4}
%   (\frac{1}{S(\dataobs)}
% -
%   \frac{1}{S(\dataobs')})
%   \big)
%   }\\
%   \end{split}
%   \end{equation*}

%   Because the property of $\gamma -$ smooth sensitivity: $\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma$ $\implies$
%   $\frac{- \epsilon}{4}
%   (\frac{1}{S(\dataobs)}-
%   \frac{1}{S(\dataobs')}) \geq \frac{- \epsilon}{4} \cdot \gamma$
%   \begin{equation*}
%   \begin{split}
%   & \leq \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
%   \frac {
%   \exp
%   \big(
%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
%   \big)
%   } 
%   {
%   \sum_{r'\in \candidateset} 
%   \exp 
%   \big(
%   \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
%   \big)
%   \exp 
%   \big(
%   \frac{-\epsilon}{4}
%   \big)
%   \exp
%   \big(
%   \frac{- \epsilon}{4} \cdot \gamma
%   \big)
%   }\\
%   & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
%   \frac {
%   \exp
%   \big(
%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
%   \big)
%   } 
%   {
%   \sum_{r'\in \candidateset} 
%   \exp 
%   \big(
%   \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
%   \big)
%   \exp 
%   \big(
%   \frac{-\epsilon}{4} +   \frac{- \epsilon}{4} \cdot \gamma
%   \big)
%   }\\
%   & = e^{( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma )} \cdot 
%   \frac {
%   \exp
%   \big(
%   \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
%   \big)
%   } 
%   {
%   \unomalizer{\dataobs'}
%   }\\
%   & = e^{( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma )} \cdot   \hexpmechPr{\dataobs'}{z = r}
%   \end{split}
%   \end{equation*}

%   Given $\gamma = 1$, $\epsilon - $differential privacy can be achieved by $\hexpmech$.

% \end{proof}

% \noindent \textbf{ Lemma \ref{lem_acc_lap}.}
% \emph{
% Given $Y \thicksim \lap{0}{b}$, the accuracy bound developed for $\lapmech$ is:
% \begin{align*}
% &
% \lapmechPr{\dataobs}{
% \begin{aligned}
% \lefteqn{\hellinger(\bysinfer{\dataobs}, z )}\\ 
% &= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
% \end{aligned}
% }
% \\
% &\qquad = 
% \begin{cases}
% \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta }} - e^{- \frac{\epsilon (t + 1)}{\Delta }}) &  t \geq 0\\
% \frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta }} - e^{\frac{\epsilon (t)}{\Delta }}) & t < 0
% \end{cases}
% \end{align*}
% where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer{\dataobs} = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $z = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
% }
